
\renewcommand{\thechapter}{}
%\cleardoublepage
%\phantomsection
%\textsc{\Large Referenser}\\[0.5cm]
\chapter{Referenser}
\begin{flushleft}
\small
Atlassian (2012) Bamboo. \emph{Continuous Integration, Continuous Deployment and Build server Atlassian  }. http://www.atlassian.com/software/bamboo/overview (2012-05-13).

Beanstalk (2007) \emph{About - beanstalkd}, http://kr.github.com/beanstalkd/ (2012-05-14).

Breit, L. (1998) Web server connectivity, performance. \emph{Unisys World}, vol. 19, nr. 7, ss. 8, 10.

Chacon, S. (2010) Smart HTTP Transport. \emph{Git}, http://git-scm.com/2010/03/04/smart-http.html (2012-05-10).

Chacon, S. (2009) \emph{Git on the Server - The Protocols. Pro Git}, Apress, New York.

Chalmers tekniska högskola (2008) \emph{Anonyma tentor}, https://student.portal.chalmers.se/sv/chalmersstudier/tentamen/Sidor/Anonyma-tentor.aspx, (2012-05-12).

Chalmers tekniska högskola (2009) \emph{Akademisk hederlighet på Chalmers – Vilka är våra spelregler?}, https://document.chalmers.se/download?docid=986701354, (2012-05-13).

Chalmers tekniska högskola (2012) Kurser på Chalmers. \emph{Sök i kursutbudet}. https://student.portal.chalmers.se/sv/chalmersstudier/minkursinformation/Sidor/SokKurs.aspx (2012-05-13).

ECMA (2011) Standard ECMA-262, \emph{ECMAScript Language Specification}, upplaga 5.1.Geneve: ECMA.

Gedell, T. (2006) \emph{Grading submissions - Review submission}, http://fire.cs.chalmers.se/doc/admin/grading-grade.html (2012-05-14).

Gedell, T. (2006) \emph{Upload File}, http://fire.cs.chalmers.se/doc/student/upload.html (2012-05-13).

Git (2012) \emph{git-clone(1) Manual Page}. http://git-scm.com/docs/git-clone (2012-05-13).

Gitorious (2007) About Gitorious. \emph{ About - Gitorious}. http://www.gitorious.org/about (2012-05-07).

GNU (2007) GNU Affero General License. \emph{GNU Affero General Public License - GNU Project - Free Software Foundation (FSF)}. http://www.gnu.org/licenses/agpl-3.0.html,(2012-05-06).

GNU (2012) What is Copyleft? \emph{What is Copyleft? - GNU Project - Free Software Foundation (FSF)}. http://www.gnu.org/copyleft/,(2012-05-06).

Internet Engineering Task Force (1999) \emph{RFC 2616 Hypertext Transfer Protocol -- HTTP/1.1}, Fielding, et al.: IETF.

Internet Engineering Task Force (2011) \emph{RFC 6455 The WebSocket Protocol} , Fette, I., Melnikov, A.: IETF.

Launchpad (2010) LaunchpadLicense. \emph{LaunchpadLicense - Launchpad Development}. https://dev.launchpad.net/LaunchpadLicense, (2012-05-14).

Launchpad (2009) Launchpad is now open source. \emph{Launchpad Blog} http://blog.launchpad.net/general/launchpad-is-now-open-source (2012-02-09).

Lilleaas, A. (2010) Work on Rails 3 upgrade has started. \emph{Work on Rails 3 upgrade has started - Google Groups}. https://groups.google.com/group/gitorious/browse\_thread/thread/16c4a60d760c0c07/ca246703db19f3ce?pli=1 (2012-05-06).

Mesbah, A., van Deursen, A. (2008) A component- and push-based architectural style for ajax applications. \emph{Journal of Systems and Software}, vol. 81, nr. 12, ss. 2194-2209.

Mlodgenski, J. (2010) PostgreSQL vs. MySQL: How to Select the Right Open-Source Database. \emph{eWeek}. 2010-10-21.  http://www.eweek.com/c/a/Linux-and-Open-Source/PostgreSQL-vs-MySQL-How-to-Select-the-Right-OpenSource-Database/ (2012-05-11).

O'Sullivan, B. (2009) Making Sense of Revision-Control Systems. \emph{Communications of the ACM}, vol. 52, nr. 9, Doi:10.1145/1562164.1562183.

Preston-Werner, T. (2011) \emph{Ten Lessons from GitHub's First Year}. http://tom.preston-werner.com/2011/03/29/ten-lessons-from-githubs-first-year.html (2012-05-13).

Rails weblog (2008) This Week in Edge Rails. \emph{Riding Rails: This Week in Edge Rails}. http://weblog.rubyonrails.org/2008/11/28/this-week-in-edge-rails/ (2012-05-12).

Redis (Okänt år) Who's using Redis?, \emph{Who's using Redis? - Redis}. http://redis.io/topics/whos-using-redis, (2012-05-16).

Rubyforge (2012) Rack::Builder. \emph{Class: Rack::Builder}. http://rack.rubyforge.org/doc/classes/Rack/Builder.html (2012-05-13).

TIOBE Software (2012) TIOBE Programming Community Index for May 2012. \emph{TIOBE Software: Tiobe Index}. http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html (2012-05-13).

URKUND. (2012) Integrera URKUND i organisationens lärplattform. \emph{Urkund}. http://www.urkund.se/SE/uoh\_integration.asp, (2012-05-13).

Vaughan-Nichols, S. (2007) Last of the GPL Licenses Goes to Version 3; The Free Software Foundation has released the GNU Affero General Public License Version 3, the open-source over-a-network license, to general use. (Linux-Watch), \emph{eWeek} (2012-05-06).

Wang, T.J. et al. (2010) Accounting For The Benefits Of Database Normalization. \emph{American Journal of Business Education}, vol. 3, nr. 1, ss. 41-52.


\normalsize
\end{flushleft}

